\documentclass[10pt, hidelinks]{article}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{array}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=10mm,
 right=20mm,
 top=10mm,
 }
\begin{document}
	% Personal Information

	\begin{minipage}[t]{0.46\textwidth}
		{\Huge\color{RoyalBlue}Firstname Surname}\\
		{\Large\textbf{I}ndian \textbf{I}nstitute of \textbf{T}echnology \textbf{G}oa}
	\end{minipage}
	\begin{minipage}[t]{0.54\textwidth}
		\begin{flushright}
			{\small
			Third Year \textbf{Undergraduate}, {\color{RoyalBlue}Electrical Engineering\\}
			{\color{RoyalBlue}Add: }{2/324 Jankipuram Vistar, Lucknow, Uttar Pradesh\\}
			{\color{RoyalBlue}E-Mail: }{\href{mailto:namami2011@gmail.com}{namami2011@gmail.com}\\}
			{\color{RoyalBlue}Mobile: }{+91 8840273138\\}
			{\color{RoyalBlue}LinkedIn: }{\href{https://www.linkedin.com/in/namamishanker/}{namami\_shanker}\\}
			{\color{RoyalBlue}GitHub: }{\href{https://www.linkedin.com/in/namamishanker/}{NamamiShanker}\\}
			}
		\end{flushright}
	\end{minipage}

	% Education Information

	{\large\color{RoyalBlue}Education}
	\par\noindent\rule[7pt]{\textwidth}{0.1pt}
	\begin{center}
		{\small \vspace*{-5mm}
		\begin{tabular}{ m{0.6\textwidth} m{0.15\textwidth} m{0.15\textwidth}}
			BTech, Electrical Engineering: Indian Institute of Technology Goa & CGPA: 8.12/10 & 2019 - PRESENT \\
			Class 12: City Montessori School & Aggregate: 97\% & 2014-2018 \\
		\end{tabular}
		}
	\end{center}

	% Experiences/Internships

	{\large\color{RoyalBlue}Experience}
	\par\noindent\rule[7pt]{\textwidth}{0.1pt}

	{\normalsize\textbf{Interned at ABC under Mr. XYZ}} {\small[\href{https://httpbin.com}{Offer Letter/LinkedIn Post/Report}]} \hspace*{8pt} {\normalsize\textit{(20XX-20XX)}}
	{\vspace*{-3mm}
	\begin{itemize}
		\itemsep-0.3em
		\item Worked on this thing for this much amount of time.
		\item Gained Industry level knowledge about this field
		\item Gained experience in this, that and these tools.
	\end{itemize}
	}
	{\normalsize\textbf{Interned at ABC under Mr. XYZ}} {\small[\href{https://httpbin.com}{Offer Letter/LinkedIn Post/Report}]} \hspace*{8pt} {\normalsize\textit{(20XX-20XX)}}
	{\vspace*{-3mm}
	\begin{itemize}
		\itemsep-0.3em
		\item Worked on this thing for this much amount of time.
		\item Gained Industry level knowledge about this field
		\item Gained experience in this, that and these tools.
	\end{itemize}
	}

	% Projects

	{\large\color{RoyalBlue}Projects}
	\par\noindent\rule[7pt]{\textwidth}{0.1pt}

	{\normalsize\textbf{Designed an Object-oriented design of digital filtering in scipy.signal}} {\small[\href{https://httpbin.com}{Offer Letter/LinkedIn Post/Report}]} \hspace*{8pt} {\normalsize\textit{(20XX-20XX)}}
	{\vspace*{-3mm}
	\begin{itemize}
		\itemsep-0.3em
		\item Worked on this thing for this much amount of time.
		\item Worked with Python, API design. Gained experience in Digital Signal Processing.
		\item Mentored by Rick Sanchez. The lead of Senate of the Ricks and intergalactic time traveller.
	\end{itemize}
	}
	{\normalsize\textbf{Created a time machine from a microwave oven and a Motorola switch phone}} {\small[\href{https://httpbin.com}{Offer Letter/LinkedIn Post/Report}]} \hspace*{8pt} {\normalsize\textit{(20XX-20XX)}}
	{\vspace*{-3mm}
	\begin{itemize}
		\itemsep-0.3em
		\item Worked creating a D-Mail machine to send message to the past for three weeks.
		\item Gained Industry level knowledge Microwave ovens, Motorola Switch Phones and Kerr Black Holes.
		\item Gained hands on experience with penetration attack, phishing, and SQL Injections attacks. And also, time travel.
	\end{itemize}
	}

	{\large\color{RoyalBlue}Skills}
	\par\noindent\rule[7pt]{\textwidth}{0.1pt}
\end{document}